Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-13 paper/paper.tex
adding R scripts

@@

\subsection{False Positives Bugs}

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory
\cite{bug4979}.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 20 0 0,clip,width=0.25\textwidth]{R/barplot}  
  \caption{\label{fig:workflow}HI and LO warnings reports by each fuzzer.}
\end{figure}

@@

\subsection{False Positives}

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory.
